\rs{Kink and fluting instabilities in a dynamically twisted flux tube}{Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity}

### 2021-10-18 paper.tex
Highlight my own comments

The helical kink instability is a form of ideal magnetohydrodynamic
(MHD) instability which occurs in highly twisted magnetic flux tubes
such as those making up much of the solar
corona~\cite{realeCoronalLoopsObservations2014} and has been well
studied in the coronal
context~\cite{hoodKinkInstabilitySolar1979,hoodCoronalHeatingMagnetic2009,browningSolarCoronalHeating2003b,barefordShockHeatingNumerical2015,quinnEffectAnisotropicViscosity2020}. Given
its energetic nonlinear development, it is considered a potential
mechanism for heating the solar corona through the theory of
nanoflares~\cite{klimchukSolvingCoronalHeating2006,browningMechanismsSolarCoronal1991}
and a key mechanism in the production of solar
flares~\cite{hoodKinkInstabilitySolar1979}. Previous work by the same
authors has investigated a twisted magnetic flux tube already linearly
unstable to the helical kink instability, \rs{investigating particularly}{focussing specifically on}
the effect of anisotropic viscosity on the nonlinear
dynamics~\cite{quinnEffectAnisotropicViscosity2020}. In~\cite{quinnEffectAnisotropicViscosity2020}
and most other investigations of the kink instability
\rs{}{e.g. \cite{hoodCoronalHeatingMagnetic2009}}, a perturbation 
is applied to an already significantly twisted flux tube. An
alternative way to excite the instability (and the way employed here)
is to start with an initially straight field and apply twisting
motions at the boundaries to form a twisted flux tube which eventually
becomes unstable. This kind of dynamic excitation of the kink
instability is useful in that it represents more closely \rs{the real
development of a magnetic flux tube and associated}{actual evolution
  of magnetic flux tubes and the associated} instabilities in 
the solar corona. \rs{The}{In our simulations, the}
dynamic twisting of the flux tube reveals an additional instability,
the \rs{fluting}{flute} instability, which has been theorised (for example,
in~\cite{priestMagnetohydrodynamicsSuna}). \jq{}{While oscillations involving flute perturbations have been found in simulations of coronal loops~\cite{terradasEffectMagneticTwist2018}, to our knowledge, this is the first time the flute \em{instability} has been investigated computationally in a coronal context.}

@@

It is prudent to ask, if the current distribution, which develops as the flux tube is twisted, is similar to that found in the initial flux tube configuration of~\cite{quinnEffectAnisotropicViscosity2020}, why do we not observe the fluting instability in~\cite{quinnEffectAnisotropicViscosity2020}? Although the current distribution (and thus heating and pressure distributions) in the tubes of~\cite{quinnEffectAnisotropicViscosity2020} may support the flute instability, the tube is initially perturbed with a motion close to an unstable eigenmode of the kink instability, resulting in the instability growing from $t=0$. In contrast, in the tubes studied here, such a perturbation must build from numerical noise, allowing a secondary, fluting perturbation to also build and become significant enough to observe.

urther detailed comparison of the models is required to fully understand this,  \todo{finish me}

>>>>

The helical kink instability is a form of ideal magnetohydrodynamic
(MHD) instability which occurs in highly twisted magnetic flux tubes
such as those making up much of the solar
corona~\cite{realeCoronalLoopsObservations2014} and has been well
studied in the coronal
context~\cite{hoodKinkInstabilitySolar1979,hoodCoronalHeatingMagnetic2009,browningSolarCoronalHeating2003b,barefordShockHeatingNumerical2015,quinnEffectAnisotropicViscosity2020}. Given
its energetic nonlinear development, it is considered a potential
mechanism for heating the solar corona through the theory of
nanoflares~\cite{klimchukSolvingCoronalHeating2006,browningMechanismsSolarCoronal1991}
and a key mechanism in the production of solar
flares~\cite{hoodKinkInstabilitySolar1979}. Previous work by the same
authors has investigated a twisted magnetic flux tube already linearly
unstable to the helical kink instability, \rs{investigating particularly}{focussing specifically on}
the effect of anisotropic viscosity on the nonlinear
dynamics~\cite{quinnEffectAnisotropicViscosity2020}. In~\cite{quinnEffectAnisotropicViscosity2020}
and most other investigations of the kink instability
\rs{}{e.g. \cite{hoodCoronalHeatingMagnetic2009}}, a perturbation 
is applied to an already significantly twisted flux tube. An
alternative way to excite the instability (and the way employed here)
is to start with an initially straight field and apply twisting
motions at the boundaries to form a twisted flux tube which eventually
becomes unstable. This kind of dynamic excitation of the kink
instability is useful in that it represents more closely \rs{the real
development of a magnetic flux tube and associated}{actual evolution
  of magnetic flux tubes and the associated} instabilities in 
the solar corona. \rs{The}{In our simulations, the}
dynamic twisting of the flux tube reveals an additional instability,
the \rs{fluting}{flute} instability, which has been theorised (for example,
in~\cite{priestMagnetohydrodynamicsSuna}). \jq{}{While oscillations involving flute perturbations have been found in simulations of coronal loops~\cite{terradasEffectMagneticTwist2018}, to our knowledge, this is the first time the flute instability has been investigated computationally in a coronal context.}

@@

\jq{}{It is prudent to ask, if the current distribution, which develops as the flux tube is twisted, is similar to that found in the initial flux tube configuration of~\cite{quinnEffectAnisotropicViscosity2020}, why do we not observe the fluting instability in~\cite{quinnEffectAnisotropicViscosity2020}? Although the current distribution (and thus heating and pressure distributions) in the tubes of~\cite{quinnEffectAnisotropicViscosity2020} may support the flute instability, the tube is initially perturbed with a motion close to an unstable eigenmode of the kink instability, resulting in the instability growing from $t=0$. In contrast, in the tubes studied here, such a perturbation must build from numerical noise, allowing a secondary, fluting perturbation to also build and become significant enough to observe.}
